### 1.Rank function:
```{r}
x <- c(2,7,1,-17,NA,Inf,35,21)
```

Use Rank function in R with NAs as last
```{r}
rank(x,na.last = TRUE)
```

Use Rank function in R with NAs as first
```{r}
rank(x,na.last = FALSE)

```

### 2. What does below function do?
rowSums function adds all the values present in each rows separately 
```{r}
rowSums(iris[,-5])
```

### 3. What does below function do?
colSums function adds all the values present in each columns separately 
```{r}
colSums(iris[,-5])

```

### 4. what does below piece of code do?
```{r}
z = c("may", "the", "rain", "shower")
substring(z, 2, 3) <- c("@", "#")
```
* Substring function will extract or replace the substrings in a character vector.
* First 2 letters of all the elements in the character vector z is replaced with the values {c("@","#")} successively since the start value in substring is given as 2 
* letters more than 3 will not be displayed since the last value in substring is given as 3 
* So the output of this code will be: "@y","#e","@i","#o"

### 5. what does below function do?
```{r}
v1 <- c(2,5,6,3,7)
v2 <- c(15,16,7,3,2,7,5)
match(v1,v2)
```
* Match returns a vector of the positions of first matches of its first argument(v1) in its second (v2).
* If no match is found then NA will be returned. In this case 2 (v1) is found in 5th position of 2nd argument(v2) so 5 will be returned
* Output of this would be 5 7 NA 4 3

### 6.Sort mtcars by mpg column and sort mtcars by carb  and then by cyl
```{r}
data(mtcars)
mpg1<-mtcars[order(mtcars$mpg),]
carb1<-mtcars[order(mpg1$carb),]
finalData <- mtcars[order(carb1$cyl),]
print(finalData)
```
### 7. Use identical functions and check if below vectors are equal
```{r}
a <- c(1,2,4,5)
b <- c(1,5,4,2)
identical(a,b)
```
### 8.Create a function that given one word, return the position of word’s letters on letters vector.
```{r}
fun <- function(x){
  match(unlist(strsplit(x, split="")), letters)
}
fun("acd")
```
### 9.Create a function that given a numeric vector X returns the digits 0 to 9 that are not in X.
```{r}
num <- function(y){
  x<-setdiff(0:9,y)
  return(x)
}
num(c(1,3,5,7))
```

### 10. Create a function that given a numeric vector, sort this in ascending order and duplicate it by two.
```{r}
dup <- function(AS){
  AS1<-sort(AS,decreasing = FALSE)
  final<-rep(AS1,each=2)
  return (final)
}
dup(c(3,5,6,2,8,91))
```
### 11. Consider a data frame df:
###Create a function that, given a data frame and two indexes, exchanges two values ??of the Code variable with each other.

```{r}
Id=c(1:10)
Age=c(14,12,15,10,23,21,41,56,78,12)
Sex=c('F','M','M','F','M','F','M','M','F','M')
Code=letters[1:10]
df=data.frame(Id,Age,Sex,Code)

swap <- function(x1,x3){
  df1<-paste(df[x1,'Id'])
  df[x1,'Id']<-paste(df[x3,'Id'])
  df[x3,'Id']<-paste(df1)
  print(df[x1,'Id'])
  print(df[x3,'Id'])
}
swap(1,3)
```

### 12.Consider a vector...Create a function that given a vector string ST return a matrix:

```{r}  
x<-c('NAME:Maria /COUNTRY:uruguay /EMAIL:mariaUY@gmail.com','NAME:Paul/COUNTRY:UK /EMAIL:PaulUK@gmail.com',
       'NAME:Jhon /COUNTRY:USA /EMAIL:JhonUSA@gmail.com','NAME:Carlos /COUNTRY:Spain /EMAIL:CarlosSP@gmail.com')

mat <- function(ST){
  ST1<-gsub(":",",",ST)
  ST2<-gsub("/",",",ST1)
  ST3<-strsplit(ST2,split = ",",fixed = TRUE)
  s<-list(unique(unlist(ST3)))
  Names<-s[[1]][c(1,2,7,10,13)]
  Country<- s[[1]][c(3,4,8,11,14)]
  Email <- s[[1]][c(5,6,9,12,15)]
  m<-matrix(c(Names,Country,Email),nrow = 3,ncol = 5,byrow = TRUE)
  return(m)
}
mat(x)
```

